Counterexample-guided Synthesis \\ of Closed-loop Digital Control Systems

### 2016-09-23 paper/paper.tex
title
nudges

\title{Synthesising and Verifying Closed-loop Digital Control Systems}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

@@

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as

\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}

\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$ and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits of the integer and fractional part, respectively. Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it i.e.}, a continuous model of the plant must be discretized to obtain the discrete equivalent coefficients $b$ and $a$~\cite{Astrom08}. Although there are several discretization methods available in the literature~\cite{Franklin15}, the zero-order hold (ZOH) discretization is more suitable for representing the sampling processes that are typically employed by hybrid systems~\cite{istepanian2012digital}.

Let $C(z)$ and $G(z)$ transfer functions be arranged in vectors $c_0$ and $g_0$, respectively.
For each $C(z)$ implementation, there is a function $FWL[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller $C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable real numbers in the chosen implementation format \param{N_C}{M_C}. The quantized controller parameters vector ($c$) is generated via $FWL[c_0]$. The uncertain plant parameters ($g$) can be expressed as

\begin{equation}
g = g_0 + \Delta{g} = \left [
				\begin{tabular}{c}
				$b_{0}+\Delta{b_{0}} ~ b_{1}+\Delta{b_{1}} ~ ... ~ b_{M_G}+\Delta{b_{M_G}}$ \\%~ 
				$a_{0}+\Delta{a_{0}} ~ a_{1}+\Delta{a_{1}} ~ ... ~ a_{N_G}+\Delta{a_{N_G}}$
				\end{tabular}
				\right ],
\end{equation}

@@

DSVerifier verification flow is shown in Fig.~\ref{DSVerifier_process}. 
Steps from $1$ to $5$ are performed by users and Steps A to D are
automatically performed by DSVerifier, which accepts the digital controller
transfer functions together with the plant model.  For any digital
controller, implementation details should be provided ({\it e.g.}, number of
bits, realization, and sample time).

@@

In Step $1$, the user provides inputs $g_0$ and $\Delta{g}\%$ ({\it i.e.},
percentage form of $\Delta{g}$), which contain the plant model and the
interval, respectively.  In Step $2$, a digital controller must be designed
with any preferred method, where $c_0$ is obtained.  The controller
numerical representation and realization form are chosen in Steps $3$ and
$4$, respectively.  In Step $5$, the user finally configures the
verification parameters ({\it e.g.}, verification time, properties, and BMC
tool).  After that, DSVerifier verification engine performs an (automatic)
verification of the desired property $\phi$ ({\it i.e.}, stability).  The
user steps described in Steps $1$-$5$ results in an ANSI-C code that should
be used as an input for DSVerifier.

In Step A, DSVerifier constructs a non-deterministic model to represent the
plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
provided in Step $1$.  DSVerifier then formulates $FWL[\cdot]$ in Step B
using implementation details provided from Steps $2$ and $3$, and then
computes $FWL[c_0]$ in Step C.  Thus, DSVerifier builds an intermediate
ANSI-C code for the digital system implementation, which is used as input
for the model-checker, as pointed in Step D.

>>>>

\title{Counterexample-guided Synthesis \\
of Closed-loop Digital Control Systems}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

\author{Author names omitted for review}

@@

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits
of the integer and fractional part, respectively.  Note that $G(z)$ is a
discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
model of the plant must be discretized to obtain the discrete equivalent
coefficients $b$ and $a$~\cite{Astrom08}.  Although there are several
discretization methods available in the literature~\cite{Franklin15}, the
zero-order hold (ZOH) discretization is more suitable for representing the
sampling processes that are typically employed by hybrid
systems~\cite{istepanian2012digital}.

Let $C(z)$ and $G(z)$ transfer functions be arranged in vectors $c_0$ and
$g_0$, respectively.  For each $C(z)$ implementation, there is a function
$\mathit{FWL}[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow
Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller
$C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable
real numbers in the chosen implementation format \param{N_C}{M_C}.  The
quantized controller parameters vector ($c$) is generated via
$\mathit{FWL}[c_0]$.  The uncertain plant parameters ($g$) can be expressed
as
%
\begin{equation}
g = g_0 + \Delta{g} = \left [
				\begin{tabular}{c}
				$b_{0}+\Delta{b_{0}} ~ b_{1}+\Delta{b_{1}} ~ ... ~ b_{M_G}+\Delta{b_{M_G}}$ \\%~ 
				$a_{0}+\Delta{a_{0}} ~ a_{1}+\Delta{a_{1}} ~ ... ~ a_{N_G}+\Delta{a_{N_G}}$
				\end{tabular}
				\right ],
\end{equation}

@@

The DSVerifier verification flow is illustrated in
Fig.~\ref{DSVerifier_process}.  Steps $1$ to $5$ are performed by users and
Steps A to D are automatically performed by DSVerifier, which accepts the
digital controller transfer functions together with the plant model.  For
any digital controller, implementation details should be provided ({\it
e.g.}, number of bits, realization, and sample time).

@@

In Step $1$, the user provides inputs $g_0$ and $\Delta{g}\%$ ({\it i.e.},
percentage form of $\Delta{g}$), which contain the plant model and the
interval, respectively.  In Step $2$, a digital controller must be designed
with any preferred method, where $c_0$ is obtained.  The controller
numerical representation and realization form are chosen in Steps $3$ and
$4$, respectively.  In Step $5$, the user finally configures the
verification parameters ({\it e.g.}, verification time, properties, and BMC
tool).  After that, DSVerifier verification engine performs an (automatic)
verification of the desired property $\phi$ ({\it i.e.}, stability).  The
user steps described in Steps $1$--$5$ result in an ANSI-C code that should
be used as an input for DSVerifier.

In Step A, DSVerifier constructs a non-deterministic model to represent the
plant family $\mathfrak{G}$ using $g_0$ and $\Delta{g}\%$, which are
provided in Step $1$.  DSVerifier then formulates $\mathit{FWL}[\cdot]$ in
Step B using implementation details provided from Steps $2$ and $3$, and
then computes $\mathit{FWL}[c_0]$ in Step C.  Thus, DSVerifier builds an
intermediate ANSI-C code for the digital system implementation, which is
used as input for the model-checker, as pointed in Step D.
